Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-08 article.tex
Rename shaded code environments

\usepackage{fancyvrb}
\newenvironment{Shaded}
{\begin{tcolorbox}[title=input,boxrule=0pt]}
{\end{tcolorbox}}
\newenvironment{Shaded2}
{\begin{tcolorbox}[title=output,boxrule=0pt]}
{\end{tcolorbox}}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.13,1.00}{#1}}
\newcommand{\ClassTok}[1]{\textcolor[rgb]{0.27,0.56,0.65}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.06,0.50}{#1}}
\newcommand{\ValueTok}[1]{\textcolor[rgb]{0.13,0.57,0.41}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.47,0.37,0.15}{#1}}
\newcommand{\IDETok}[1]{\textcolor[rgb]{0.58,0.58,0.58}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.06,0.50}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.70,0.27,0.27}{#1}}

>>>>

\usepackage{fancyvrb}
\newenvironment{CodeInput}
{\begin{tcolorbox}[title=input,boxrule=0pt]}
{\end{tcolorbox}}
\newenvironment{CodeOutput}
{\begin{tcolorbox}[title=output,boxrule=0pt]}
{\end{tcolorbox}}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.13,1.00}{#1}}
\newcommand{\ClassTok}[1]{\textcolor[rgb]{0.27,0.56,0.65}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.06,0.50}{#1}}
\newcommand{\ValueTok}[1]{\textcolor[rgb]{0.13,0.57,0.41}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.47,0.37,0.15}{#1}}
\newcommand{\IDETok}[1]{\textcolor[rgb]{0.58,0.58,0.58}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.06,0.50}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.70,0.27,0.27}{#1}}
